### 2020-05-16 learning Logic/draft.tex
a

\newcommand{\jana}[1]{{\color{magenta} #1}}

@@

\begin{figure}
	\centering
	\includegraphics[width=\linewidth]{Fig/product3} \caption{Product automaton after 3 iterations}
	\label{fig:product3}
\end{figure}
\end{document}

>>>>

\newcommand{\jana}[1]{{\color{magenta} #1}}
\newcommand{\kush}[1]{{\color{blue} #1}}

@@

For the example given in Figure \ref{fig:office}, without considering $wall$ atomic proposition, it was taking approx. 15 seconds to do everything. There is some room for improvement and it might get reduced to approx. 10 seconds.

\begin{figure}
	\centering
	\includegraphics[width=\linewidth]{Fig/product3} \caption{Product automaton after 3 iterations}
	\label{fig:product3}
\end{figure}

\vspace{20pt}
\textbf{Points from the discussion on 13.05.2020:}
	\begin{itemize}
		\item We assume that the robot has the labelling of the whole system beforehand for now. We can consider the other case later.
		\item Use RRG instead of RRT so that we can go back also.
		\item \textbf{What we need from the SAMPLE procedure:} Given a pair of set of states (fromStates, toStates) in the abstract system (a formula over the APs), SAMPLE should return a newly sampled transition from a state where 'fromState' is \textit{true} to a state where 'toState' is \textit{true}. It maybe the case that such a transition doesn't exist or probability of it being sampled is very small, in that case, return \emph{null} after some given threshold time/samples.
		\item \textbf{Jan's idea:} We can keep track of the sampled transitions till now and get their ranking (finding ranking for each sampled transition will require some time because it might have to pass through the whole list of 'reachableStates'). Sample 50 (some threshold) transitions and add the one with the best rank. \kush{What will happen to the other transitions? Would we keep all of them in the memory (maintain a min-heap maybe)?}
	\end{itemize}

\end{document}
